### 2012-09-22 doc/prelim/document/chapters/nonlinear_problem/nonlinear_problem.tex
nonlinear updates

\section{Inexact Newton Methods}
\label{sec:newton_methods}
Inexact Newton methods arise when the Jacobian operator is not exactly
inverted, resulting in an inexact Newton correction as initially
described by Dembo and others \citep{dembo_inexact_1982}. For common
sparse nonlinear systems, which in turn yield a sparse Jacobian
matrix, this situation occurs when conventional iterative methods are
applied. In their definition, Dembo formulated inexact methods such
that they are independent of the linear method used to solve for the
Newton correction and therefore are amenable to use with any linear
solver.

\subsection{Newton-Krylov Methods}
\label{subsec:newton_krylov_methods}
A form of inexact Newton methods, \textit{Newton-Krylov methods} are
nonlinear iterative methods that use a Krylov subspace method as the
linear solver for generating the Newton correction. As we investigated
in Chapter~\ref{ch:linear_problem}, Krylov methods are robust and
enjoy efficient parallel implementations. Furthermore, their lack of
explicit dependence on the operator make them easier to implement than
other methods.

\subsubsection{Choosing a Krylov Method}
\label{subsubsec:krylov_choice}
From their numerical studies, McHugh and Knoll found
that the robustness enjoyed by the long recurrence relations used by
GMRES for the orthogonalization procedure proved to be a better choice
for use with Newton's method
\citep{mchugh_inexact_1993,knoll_newton-krylov_1995}.

>>>>

\section{Inexact Newton Methods}
\label{sec:newton_methods}
Inexact Newton methods arise when the Jacobian operator is not exactly
inverted, resulting in an inexact Newton correction as initially
described by Dembo and others \citep{dembo_inexact_1982}. For common
sparse nonlinear systems, which in turn yield a sparse Jacobian
matrix, this situation occurs when conventional iterative methods are
applied. In their definition, Dembo formulated inexact methods such
that they are independent of the linear method used to solve for the
Newton correction and therefore are amenable to use with any linear
solver. Furthermore, they bind the convergence of the outer nonlinear
iteration to the inner linear iteration such that:
\begin{equation}
  ||\ve{J}(\ve{u}^k)\delta \ve{u}^k + \ve{F}(\ve{u}^k)|| \leq \eta^k
  ||\ve{F}(\ve{u}^k)||\:,
  \label{eq:inexact_newton_forcing}
\end{equation}
where $\eta^k$ is defined as the \textit{forcing term} at the $k$
iterate. Eq~(\ref{eq:inexact_newton_forcing}) then states that the
residual generated by the linear residual is bound by the nonlinear
residual and how tightly it is bound is defined by the forcing
term. This is useful in that we can vary how tightly coupled the
Newton correction is to the nonlinear iteration by relaxing or
tightening the convergence properties on the linear iterative
method. As a result strategies for determining the forcing term can
vary depending on the problem type \citep{eisenstat_choosing_1996}.

\subsection{Newton-Krylov Methods}
\label{subsec:newton_krylov_methods}
A form of inexact Newton methods, \textit{Newton-Krylov methods} are
nonlinear iterative methods that leverage a Krylov subspace method as
the linear solver for generating the Newton correction. As we
investigated in Chapter~\ref{ch:linear_problem}, Krylov methods are
robust and enjoy efficient parallel implementations. Furthermore,
their lack of explicit dependence on the operator make them easier to
implement than other methods.

With many Krylov methods available, which to use with the Newton
method is dependent on many factors including convergence rates and
memory usage. From their numerical studies, McHugh and Knoll found
that the robustness enjoyed by the long recurrence relations used by
GMRES for the orthogonalization procedure proved to be a better choice
for use with Newton's method
\citep{mchugh_inexact_1993,knoll_newton-krylov_1995}.
